BlogForever Crawler: Techniques and Algorithms to Harvest the Modern Web

### 2013-11-01 tex/0-abstract.tex
First abstract draft.

This paper provides a sample of a \LaTeX\ document which conforms to
the formatting guidelines for ACM SIG Proceedings.
It complements the document \textit{Author's Guide to Preparing
ACM SIG Proceedings Using \LaTeX$2_\epsilon$\ and Bib\TeX}. This
source file has been written with the intention of being
compiled under \LaTeX$2_\epsilon$\ and BibTeX.

The developers have tried to include every imaginable sort
of ``bells and whistles", such as a subtitle, footnotes on
title, subtitle and authors, as well as in the text, and
every optional component (e.g. Acknowledgments, Additional
Authors, Appendices), not to mention examples of
equations, theorems, tables and figures.

To make best use of this sample document, run it through \LaTeX\
and BibTeX, and compare this source code with the printed
output produced by the dvi file.

>>>>

Blogs are by nature a very dynamic and volatile communication medium. The BlogForever project aims to provide a generic platform for blog preservation. This paper presents a key component of this archiving system: the Web Crawler. More precisely, our discussion will concentrate on techniques to automaticaly extract content, authors, date and comments of blog posts.

Web technologies are evolving very rapidly. The recent trend toward using JavaScript to dynamically generate pages on the client side represent a new challenge for the web crawler. We will show how we integrated the headless web browser into the our spider to overcome these obstacles.

We present a simple and robust algorithm based on string similarity to build wrappers from web feeds. Being applicable to all posts of a blog, the resulting extraction procedure scale for large blogs.
